mir\_eval

### 2014-05-03 paper/paper.tex

The performance of an algorithm on an entire music collection for a given
measure is obtained by averaging the per-excerpt scores for that measure over
all excerpts in the collection.

>>>>

The performance of an algorithm on an entire music collection for a given
measure is obtained by averaging the per-song scores for that measure over
all songs in the collection.
